Hydra Battles and Cie

### 2021-03-09 doc/part-hydras.tex
minor improvements

Note that we did not define any function $L_\alpha$ \emph{for any $\alpha<\epsilon_0$} yet. We have got no more than a collection of proved realizations of $\texttt{L\_spec}\;\alpha$ for several values of $\alpha$.

@@

Using the \texttt{coq-equations} plug-in by 
M. Sozeau~\cite{sozeau:hal-01671777}, we will now define a function \texttt{L\_} which maps any ordinal  $\alpha<\epsilon_0$ to a proven realization of 
$\texttt{L\_spec}\;\alpha$.   
\subsection{Definition}

In order to get a total function, we use our type \texttt{E0} of well-formed ordinal terms,(see Sect~\vref{sect:E0-def}).  Our definition is structured along a well-founded recursion and
a case-study (zero, limit and successor ordinals).

@@

\label{sect:hardy}
In order to give an idea of the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}

@@

\subsection{Abstract Properties of H-functions}
~\label{sect:H-alpha-prop}

@@

Prove that for any $n\geq 2$, $\textrm{Ack}\,\,n\,n\leq  F_\omega(n)$, where \textrm{Ack} is the Ackermann function. Next, prove that $F_\alpha$ is not primitive recursive, for any $\alpha\geq\omega$  (please see Sect.~\vref{sect:ack-not-PR}).
On the other hand, please show that for any natural number $n$, the function $F_n$ is primitive recursive.

>>>>

Note that we did not define any function $L_\alpha$ \emph{for any $\alpha<\epsilon_0$} yet. We have got no more than a collection of proved realizations of $\texttt{L\_spec}\;\alpha$ for a few values of $\alpha$.

@@

Using the \texttt{coq-equations} plug-in by 
M. Sozeau~\cite{sozeau:hal-01671777}, we will now define a function \texttt{L\_} which maps any ordinal  $\alpha<\epsilon_0$ to a proven realization of 
$\texttt{L\_spec}\;\alpha$.   
To this end, we represent ordinals as inhabitants of the type 
\texttt{E0} of well-formed ordinal terms (see Sect~\vref{sect:E0-def}). So, we define a total function \texttt{L\_} of type
\texttt{E0 -> nat -> nat}, by transfinite recursion, considering the usual three cases : $\alpha=0$, $\alpha$ is a successor, $\alpha$ is a limit ordinal.

\subsubsection{Definition}

@@

\label{sect:hardy}
In order to give a feeling on  the complexity of the functions  $L_\alpha$s, we compare them with a better known family of functions, the so called \emph{Wainer-Hardy hierarchy} of fast growing functions,
presented for instance in~\cite{Promel2013}. 
\index{maths}{Rapidly growing functions!Hardy Hierarchy}

@@

\subsection{Abstract Properties of Hardy functions}
~\label{sect:H-alpha-prop}

@@

Prove that for any $n\geq 2$, $\textrm{Ack}\,\,n\,n\leq  F_\omega(n)$, where \textrm{Ack} is the Ackermann function. Next, prove that $F_\alpha$ is not primitive recursive, for any $\alpha\geq\omega$  (please see Sect.~\vref{sect:ack-not-PR}).
On the other hand, please show that for any natural number $n$, the function $F_n$ is primitive recursive.
Thus $F\_alpha$ is primitive recursive if and only if $\alpha$ is finite.
